\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2022-11-17 src/tex/ms.tex
Added plots in fitting waveform coefficients section

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{../static/amplitude_loss.pdf}
    \caption{
        Relative error of amplitudes of IMRPhenomD waveforms. Blue: Error between original Phenom waveform and NR waveform; Orange: Error between optimized waveform and NR waveform.
    }
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{../static/MM_logdiff_q148.pdf.pdf}
    \caption{
        Distribution of the log difference of mismatches between optimized and original model. The mean shows a 36\% decrease in mismatch. 
    }
\end{figure}
